---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# MSDRCapstone3

The goal of MSDRCapstone3 is to provide helper functions to read and clean NOAA significant earthquakes data for easy visual anlayses

## Installation

You can install MSDRCapstone3 from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("nobuhiroK/MSDRCapstone3")
```

## Example

This is a basic example which shows you how to solve a common problem:


load cleaned earthquaks data
```{r example, eval=FALSE}
quakes <- eq_location_clean()
```


simple timeline map 
```{r, eval=FALSE}
quakes%>%
dplyr::filter(COUNTRY %in% c('USA', 'JAPAN')) %>%
dplyr::filter(DATE > '2000-01-01') %>%
ggplot(aes(x = DATE,
           y = COUNTRY,
           color = as.numeric(TOTAL_DEATHS),
           size = as.numeric(EQ_PRIMARY)
           )) +
  geom_timeline() +
  labs(size = "Richter scale value", color = "# deaths")
```

leaflet map with DATE annotation
```{r, eval=FALSE}
quakes%>%
dplyr::filter(COUNTRY %in% c('JAPAN')) %>%
dplyr::filter(DATE > '2000-01-01') %>%
eq_map(annot_col="DATE")
```

