---
title: "Vignette for MSDR package"
author: "Nobuhiro Kikuchi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


The `MSDRCapstone3` package provides helper functions to reasd and clean NOAA significant earthquakes data for visual anlyses of timeline map and leaflet map.

You can install MSDRCapstone3 from github with:



```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("nobuhiroK/MSDRCapstone3")
```

Packages to import
```{r, eval=FALSE}
library(MSDRCapstone3)
library(dplyr)
library(magrittr)
library(ggplot2)
library(leaflet)
```

#Loading Data

row data from package data
```{r, eval=FALSE}
quakes <- read_signif()
```


row data from NOAA website
```{r, eval=FALSE}
quakes <- read_signif(URL=True)
```

cleaned data 
```{r, eval=FALSE}
quakes <- eq_clean_data()
```

cleaned location data 
```{r, eval=FALSE}
quakes <- eq_location_clean()
```

# Timeline plot 

simple timeline map 
```{r, eval=FALSE}
quakes%>%
dplyr::filter(COUNTRY %in% c('USA', 'JAPAN')) %>%
dplyr::filter(DATE > '2000-01-01') %>%
ggplot(aes(x = DATE,
           y = COUNTRY,
           color = as.numeric(TOTAL_DEATHS),
           size = as.numeric(EQ_PRIMARY)
           )) +
  geom_timeline() +
  labs(size = "Richter scale value", color = "# deaths")
```

timeline map with annotation

```{r, eval=FALSE}
quakes%>%
dplyr::filter(COUNTRY %in% c('USA', 'JAPAN')) %>%
dplyr::filter(DATE > '2000-01-01') %>%
    ggplot(aes(x = DATE,
               y = COUNTRY,
               colour = as.numeric(TOTAL_DEATHS),
               size = as.numeric(EQ_PRIMARY)))+
  geom_timeline()+
  geom_timeline_label(aes(magnitude = as.numeric(EQ_PRIMARY),label = LOCATION_NAME, n_max = 5)) +
   scale_size_continuous(name = 'Richter scale value') +
   scale_color_continuous(name = '# of Deaths') 
```
# Leaflet map

annotation with selected column 'DATE'

```{r, eval=FALSE}
quakes%>%
dplyr::filter(COUNTRY %in% c('JAPAN')) %>%
dplyr::filter(DATE > '2000-01-01') %>%
eq_map(annot_col="DATE")
```

annotation with custom made column 'popup' with eq_create_label()

```{r, eval=FALSE}
quakes %>%
dplyr::filter(COUNTRY %in% c('JAPAN')) %>%
dplyr::filter(DATE > '2000-01-01') %>%
dplyr::mutate(popup_text = eq_create_label(.)) %>%
eq_map(annot_col = "popup_text")

```

